More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-05-25 2016-Weak-FH-Bisim/WeakBisim.tex
Ludo: Task 1,2,3 (improved def and 2 new properties)

\TODO{Id(s) is the identity function on variables of state s}
\begin{definition}[Non-observability of silent actions]
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ we have
\[ \openrule
         {
           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
\end{definition}

@@

\TODO{We will discuss this corollary and the title.}

\begin{corollary}[Weak Composability]
	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
	obtain two weak FH-bisimilar pNets.
\end{corollary}

>>>>

\TODO{Id(s) is the identity function on variables of state s}
\begin{definition}[Non-observability of silent actions]
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\[ \openrule
         {
           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and for all $\alpha$, $j$, $s$, $\Post$ and $s'$ we have
\[ \openrule
         {
           (j\mapsto\tau),\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \implies \alpha=\tau\land s=s'\land \Post=\symb{Id}(s)
\]
\end{definition}

We then have the following property that justifies the fact that we can abstract away tau transitions from holes.

\begin{property}
There is an open transition from state $s$ to state $s'$ if and only if there is a sequence of open transitions from $s$ to $s'$ where all open transitions except one are of the form:\[ \openrule
         {
           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
         {s \OTarrow {\tau} s}
\]
\end{property}
\TODO{the formal view is not much interesting}

@@

\begin{property}[Weak open transition transitivity]
Let $A$ be an open automaton, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
Suppose we have the following weak open transitions in $\WT$:
\[\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1}
\qquad 
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2   }
         {s_1 \OTWeakarrow {\alpha} s_2}
\qquad
\openrule
         {
           \overline{\gamma_3},\Pred_3,\Post_3   }
         {s_2 \OTWeakarrow {\tau} s_3}
\]
Then there is ag weak  open transition of the following form in $\WT$:
\[\openrule
         {
           \overline{\gamma},\Pred,\Post   }
         {s \OTWeakarrow {\alpha} s_3}
\]
Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
\[
\begin{array}{rcl}
\gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
\Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
\Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
\end{array}\]
\end{property}

\TODO{We will discuss this corollary and the title.}
\TODO{Move the following propertiesafter the definition of Weak bisim!}
\begin{corollary}[Weak Composability]
	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
	obtain two weak FH-bisimilar pNets.
\end{corollary}
